\documentclass[a4paper,12pt]{article}

% Packages
\usepackage[default,oldstyle,scale=0.95]{opensans}
\usepackage[T1]{fontenc}
\usepackage{fontawesome} % for icons
\usepackage{titlesec} % custom \section
\usepackage{url,parskip} % packages for formating
\usepackage{multicol} % multiples columns
\usepackage{ragged2e} % for alignment
\usepackage{array} % for tabular alignment
\usepackage[hidelinks]{hyperref} % for links
\usepackage[margin=1cm]{geometry} % page margins
%\geometry{showframe} % this can be use for alignment

% CV sections
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{4pt}
\setlength{\columnsep}{1cm} % space between columns

% Commands
\newcommand{\body}[1]{
    \begin{tabular}{>{\raggedleft\bfseries\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{15cm}}
        #1
    \end{tabular}
}

% Main
\begin{document}

% Title
\par {
  {\Huge Gabriel Marin}
  \bigskip
}

% Body
\body{
% Contact
    Contact
    &\href{mailto:gbrlmarn@gmail.com}{\faicon{envelope} gbrlmarn@gmail.com}\\
    &\href{https://github.com/gbrlmarn}{\faicon{github} github.com/gbrlmarn}\\
    &\href{https://gbrlmarn.github.io}{\faicon{globe} gbrlmarn.github.io}\\
    &\href{https://linkedin.com/in/gbrlmarn}{\faicon{linkedin} linkendin.com/in/gbrlmarn}\\
    \\
% Programming Languages 
Programming Languages & C, C++, Go, Rust, Python, Java, Bash, Clojure, Lisp, Erlang, Elixir, Lua, Perl, JavaScript, Assembly, SQL. \\
\\
% Tools
Tools & Linux, Git, Coreutils, Vim, ZeroMQ, Regexp, \LaTeX, Emacs, Docker, Podman, GDB, Boost, Make, CMake, BitBake, OpenSSL, OpenWrt, HTML, CSS, RabbitMQ, Valgrind, FlatBuffers, Hugo, Terraform, Django. \\
\\
% Work 
  Work & Software Engineer at Luxoft, Bucharest 2022-Present \\
  &\footnotesize{Provided better testing tooling to at least 2 teams by developing command line application using C++ and ZeroMQ library for sending and receiving messages over TCP sockets.}\\
  &\footnotesize{Increase code coverage by minimum 75\% by creating unit tests using Boost library.}\\
  &\footnotesize{Aligned codebase in 5 projects according to coding guidelines by refactoring multiple repositories.}\\
  \\
  &Software Engineer at Continental, Sibiu 2021-2022 \\
  &\footnotesize{Enhanced C code production by working on XML generator using Java and AUTOSAR library.}\\
  \\
  & System Engineer at Ministry of Internal Affairs, Rm.Valcea 2019-2021 \\
  &\footnotesize{Reduce computer setup by 1+ hour by creating automation scripts.}\\
  \\
  & Middleware Engineer at Ministry of Internal Affairs, Bucharest 2018-2019 \\
  &\footnotesize{Give access to at least 80 users in Oracle SQL database by changing permissions according to requirements.}\\
  \\
  % Open Source
  Open Source & \href{https://github.com/curl/curl}{Curl} \\
  & \footnotesize{Improved code formatting with 17 new findings by adding check for spaces around ternary operators using Perl.}\\
    \\
    & \href{https://github.com/max-niederman/ttyper}{Ttyper} \\
    & \footnotesize{Supplied application customization by solving 1 issue and implementing a functionality that permits to change the corners shape using Rust.}\\
    \\
% Education
  Education & Master's Degree in Telecommunications Engineering \\
  & Military Technical Academy, Bucharest 2018-2020 \\
  \\
  & Bachelor's Degree in Telecommunications Engineering \\
  & Military Technical Academy, Bucharest 2014-2018\\
  \\
    % Languages
    Languages & Romanian, English, Italian, French
}
\end{document}
