% Created 2024-10-08 Tue 00:59
% Intended LaTeX compiler: xelatex
\documentclass[a4paper,12pt]{article}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=2cm]{geometry}
\usepackage{fontspec}
\setmainfont{Inter}
\pagenumbering{gobble}
\usepackage{titlesec} % custom \section
\usepackage{url,parskip} % packages for formating
\usepackage{color}
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}
\titleformat{\section}{\LARGE\center}{\thesection}{}{}
\titlespacing{\section}{0pt}{4pt}{0pt}
\setlength{\columnsep}{0cm} % space between columns
\titleformat{\subsection}{\normalsize\center}{\thesubsection}{}{}[\hrule]
\titlespacing{\subsection}{0pt}{1pt}{1pt}
\titleformat{\subsubsection}{\normalsize\raggedright}{\thesubsubsection}{}{}
\titlespacing{\subsubsection}{0pt}{1pt}{0pt}
\usepackage{enumitem}
\setlist{noitemsep, leftmargin=0.5cm}
\date{}
\title{}
\hypersetup{
 pdfauthor={gbrlmarn},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.5.5)}, 
 pdflang={English}}
\begin{document}

\section*{\textbf{Gabriel Marin}}
\label{sec:org2a9ab6f}
\begin{center}
\begin{tabular}{lll}
\href{mailto:marin.gabriel@protonmail.com}{marin.gabriel@protonmail.com} & \href{https://github.com/gbrlmarn}{github.com/gbrlmarn} & \href{https://linkedin.com/in/maringabriel}{linkedin.com/in/maringabriel}\\
\end{tabular}
\end{center}
\subsection*{\textbf{Skills}}
\label{sec:org6b0e19f}
Programming Languages: C, C++, Clojure, Go, Java, Lisp, Rust,
Bash, HTML, CSS, \LaTeX{}, Erlang, Elixir, C\#, SQL, NoSQL, Datomic\\
Tools: Linux, Git, Emacs, Coreutils, Docker, Boost, Vim, ZeroMQ,
RabbitMQ, Django, Hugo, React
\subsection*{\textbf{Work Experience}}
\label{sec:org814bfb4}
\subsubsection*{\textbf{Luxoft}, Software Engineer \hfill 2022 -- Present}
\label{sec:org5fa85ea}
\begin{itemize}
\item Provided better testing tooling to at least 2 other teams by developing command line
application using C++ and ZeroMQ library for sending/receiving messages over TCP sockets.
\item Increase code coverage by minimum 75\% by creating unit tests using Boost library.
\item Aligned codebase in 5 projects according to coding guidelines
by refactoring multiple repositories.
\end{itemize}
\subsubsection*{\textbf{Continental}, Software Engineer \hfill 2021 -- 2022}
\label{sec:org0e0663b}
\begin{itemize}
\item Enhanced C code production by working on XML generator using Java and AUTOSAR library.
\end{itemize}
\subsubsection*{\textbf{Ministry of Internal Affairs}, System Engineer \hfill 2019 -- 2021}
\label{sec:orgb36cc9f}
\begin{itemize}
\item Reduce software install time by more than 1 hour on a new PC by creating automation scripts.
\end{itemize}
\subsubsection*{\textbf{Ministry of Internal Affairs}, Middleware Engineer \hfill 2018 -- 2019}
\label{sec:orgcdf6816}
\begin{itemize}
\item Give access to at least 80 users in Oracle SQL database by changing permissions according
to requirements.
\end{itemize}
\subsection*{\textbf{Open Source Experience}}
\label{sec:org789a2d7}
\subsubsection*{\textbf{Curl} \hfill \href{https://github.com/curl/curl}{curl}}
\label{sec:org469098c}
\begin{itemize}
\item Improved code checking with 17 new findings by adding functionality
that checks for spaces around ternary operators using Perl.
\end{itemize}
\subsubsection*{\textbf{Ttyper} \hfill \href{https://github.com/maxniederman/ttyper}{ttyper}}
\label{sec:org17f682a}
\begin{itemize}
\item Resolved one issue by implementing a functionality that permits to change the shape of the corners using Rust.
\end{itemize}
\subsection*{\textbf{Education}}
\label{sec:org59497bd}
\subsubsection*{\textbf{Military Technical Academy}, Bucharest \hfill 2018 -- 2020}
\label{sec:org405366f}
MA Telecommunications Engineering
\subsubsection*{\textbf{Military Technical Academy}, Bucharest \hfill 2014 -- 2018}
\label{sec:org93c5c51}
BA Telecommunications Engineering
\subsection*{\textbf{Other Skills}}
\label{sec:orgc71638d}
Languages: Romanian, English, Italian, French
\end{document}
